---
title: "Add a Title Here"
author: "Your Name Here"
date: "`r Sys.Date()`"
output: pdf_document
#output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/hannahfrank/StatsI_Fall2023_prep")
```

## Introduction

Give a brief introduction of the research question(s), and how you will answer them.

## Data

Import the data and describe it. Include below a brief written interpretation. 

```{r}
# Load data 
df <- read.csv("datasets/fictional_data.csv")
```

## Analysis

Describe how you analysed the data. You can embed R outputs directly in your text, for example, the mean of university level education is `r round(mean(df$edu),2)` years. 

Present a relevant visualization for the distribution of income. 

```{r}

```

Include some analysis of how confident we can be about our estimate for the population mean.

```{r}

```

Is there a relationship between education and income?

```{r}

```

## Conclusion

What is your main finding? What weaknesses might there be in your research? What further analyses are needed?